---
title: "hgchmagic-bar-plots"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{hgchmagic-bar-plots}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(hgchmagic)
```

## Introduction

hgchmagic has a set of functions to assists users when plotting data. Here you´ll see how to use it.


### Bar plots

The core function to plot a bar plot with hgchmagic is `hgch_bar()`

```{r}
data <- ggplot2::diamonds
data <- dsdataprep::aggregation_data(data = data,
                                       agg = "sum",
                                       group_var = "cut",
                                       to_agg = "price")

hgch_bar(data, 
         var_cat = "cut", 
         var_num = "price")
```

Plots with hgchmagic can be easily improved by adding some labels of information like titles, subtitles, caption, etc.:

```{r}
### hgch_bar_Cat()
data <- ggplot2::diamonds |> 
  dplyr::select(cut, dplyr::everything())

## Ops list
ops <- list(title = "This is a title",
            subtitle = "This is a subtitle",
            caption = "A caption? Yes, this is a caption",
            hor_title = "Categories",
            ver_title = "Numbers",
            bar_orientation = "hor")

# Plot
hgch_bar(data, 
         var_cat = "cut", 
         var_num = "price", 
         opts =  ops)
```

<br>

hgchmagic can help you plotting identifying different types of variables in the data frame. For example, when having a Categorical variable the `hgch_bar_Cat()` function could be more helpful:

```{r}
### hgch_bar_Cat()
hgch_bar_Cat(data, 
             opts = ops, 
             palette_colors = "#ffa92a")
```

More functions that plots according to variable types:

```{r}
data <- ggplot2::diamonds |> 
  select(cut, color, price, everything())

hgch_bar_CatCat(data, 
                opts = ops)
```

```{r}
hgch_bar_CatCatNum(data, 
                   opts = ops)
```

<br>

Plots with custom theme setted on _opts_ argument:
```{r}
# Data
data <- ggplot2::diamonds |> 
  select(cut, everything())

# opts from theme (canvas)
test_theme <- list(
  theme = list(
    background_color = "#2f2f2f",
    plot_margin_bottom = 30,
    plot_margin_left = 30,
    plot_margin_right = 30,
    plot_margin_top = 30,
    plot_background_color = "#f2f2f2",
    plot_border_color = "#ff2c2f",
    plot_border_size = 3,
    text_family = "ubuntu",
    text_size = 15
  )
)

# Plot
hgch_bar_Cat(data, opts = test_theme)
```

